Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-06-10 ms.tex
referee report notes

@@

\begin{abstract}
The extended \kep\ mission, \KT, is now providing photometry of new fields every
three months in a search for transiting planets.
In a recent study, Foreman-Mackey and collaborators presented a list of 36 planet
candidates orbiting 31 stars in \KT\ \Ci.
In this contribution, we present stellar and planetary properties for all systems.
We combine ground-based seeing-limited survey data and
adaptive optics imaging with an automated transit analysis scheme to validate
\Nvalidated\ candidates as planets
and identify \Nfp\ candidates as likely false positives.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a $2.24 \pm 0.25 R_\odot$ planet with $T_{eq} = 271 \pm 16$ K and an
orbital period of 33 days.
We also present two new open-source software packages that enabled this analysis:
\texttt{isochrones}, a flexible tool for fitting theoretical stellar
models to observational data to determine stellar properties; and
\texttt{vespa}, a new general-purpose procedure to calculate false positive probabilities
and statistically validate transiting exoplanets.
\end{abstract}

@@

In this work, we use grids from the Dartmouth Stellar
Evolution Database \citep{Dotter08} at solar values of \afe=$0.0$ and
helium abundance $Y=0.2741$, which come packaged with the \texttt{isochrones}
module.
We then run an MCMC chain using \texttt{emcee} \citep{Foreman-Mackey12},
an implementation of the affine-invariant ensemble sampler of
\citet{Goodman10}
for each host star conditioned on the observed
photometric properties as presented in Table 1.
We include a prior on stellar metallicity representative of the observed metallicities
of stars within 1 kpc of the Sun, following the results of \citet{Hayden15}, and a Salpeter-slope
prior on mass (up to the maximum mass available in the model grids of $3.7$ $M_\odot$).

@@

In order to account for the effects of model uncertainties, we also run
MCMC chains with photometric errors inflated artificially by a factor of three.
The observed photometric parameters are then consistent with spectroscopically-derived
parameters for stars with published spectra, and consistent with typical uncertainties
from photometric data \citep[e.g.][]{Huber14}.
We provide full chains using both inflated and un-inflated
uncertainties,\footnote{\url{http://www.astro.princeton.edu/~tdm/k2/}}
though in the rest of this work (and in Table 2) we adopt
the results obtained using the inflated values.

@@

In \paperit, only parameters directly observable from the \KT\ light curve
itself were reported: the period, time of transit center, and transit depth.
With stellar properties now in hand, we can convert these observational
results into fundamental parameters of each planet candidate.
For each candidate, we fit the light curve using a physical transit model
\citep{Mandel02, Kipping10b} simultaneously with the systematics model
described by \paperit.
We use \texttt{emcee} to sample from the posterior probability distribution
for the stellar---limb darkening coefficients, mass, radius, and effective
temperature---and planetary---radius, period, phase, impact parameter,
eccentricity, and argument of periapsis---parameters, conditioned on the
light curve and the measured stellar properties.
Following \paperit, the likelihood function that we use is marginalized over
the parameters of the systematics model.
To incorporate the stellar measurements, we approximate the constraints using
a three-dimensional Gaussian in mass, radius, and effective temperature.

@@

\acknowledgements
We thank Roberto Sanchis-Ojeda (Berkeley), Dan Huber (Sydney) and
Jeff Coughlin (SETI) for
conversations and suggestions which improved the quality of this manuscript.

>>>>

\newcommand{\change}[1]{\textbf{#1}}

@@

\begin{abstract}
The extended \kep\ mission, \KT, is now providing photometry of new fields every
three months in a search for transiting planets.
In a recent study, Foreman-Mackey and collaborators presented a list of 36 planet
candidates orbiting 31 stars in \KT\ \Ci.
In this contribution, we present stellar and planetary properties for all systems.
We combine ground-based seeing-limited survey data and
adaptive optics imaging with an automated transit analysis scheme to validate
\Nvalidated\ candidates as planets
and identify \Nfp\ candidates as likely false positives.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \change{$2.24 \pm 0.25$ $R_\oplus$} planet with $T_{eq} = 271 \pm 16$ K and an
orbital period of 33 days.
We also present two new open-source software packages that enabled this analysis:
\texttt{isochrones}, a flexible tool for fitting theoretical stellar
models to observational data to determine stellar properties, and
\texttt{vespa}, a new general-purpose procedure to calculate false positive probabilities
and statistically validate transiting exoplanets.
\end{abstract}

@@

In this work, we use grids from the Dartmouth Stellar
Evolution Database \citep{Dotter08} at solar values of \afe=$0.0$ and
helium abundance $Y=0.2741$, which come packaged with the \texttt{isochrones}
module.
\change{We then run an MCMC chain using \texttt{MULTINEST} \citep{Feroz09},
an implementation of a multimodal nested sampling algorithm,}
for each host star conditioned on the observed
photometric properties as presented in Table 1.
We include a prior on stellar metallicity representative of the observed metallicities
of stars within 1 kpc of the Sun, following the results of \citet{Hayden15}, and a Salpeter-slope
prior on mass (up to the maximum mass available in the model grids of $3.7$ $M_\odot$).

@@

As our stellar results are model-dependent, we caution users who intend to use these 
parameters for other works, such as exoplanet population studies. When available, 
stellar parameters inferred through other techniques such as asteroseismology or 
spectroscopy should supersede these values. 
The observed photometric parameters  then consistent with spectroscopically-derived
parameters for stars with published spectra, and consistent with typical
model-dependent uncertainties
from photometric data \citep[e.g.][]{Huber14}.
We provide full samples of our posteriors on the physical parameters for each 
star\footnote{\url{http://www.astro.princeton.edu/~tdm/k2/}}.

@@

In \paperit, only parameters directly observable from the \KT\ light curve
itself were reported: the period, time of transit center, and transit depth.
With stellar properties now in hand, we can convert these observational
results into fundamental parameters of each planet candidate.
For each candidate, we fit the light curve using a physical transit model
\citep{Mandel02, Kipping10b} simultaneously with the systematics model
described by \paperit.
We use \texttt{emcee} \citep{Foreman-Mackey12}, an implementation of the
affine-invariant ensemble sampler of \citep{Goodman10}
 to sample from the posterior probability distribution
for the stellar---limb darkening coefficients, mass, radius, and effective
temperature---and planetary---radius, period, phase, impact parameter,
eccentricity, and argument of periapsis---parameters, conditioned on the
light curve and the measured stellar properties.
Following \paperit, the likelihood function that we use is marginalized over
the parameters of the systematics model.
To incorporate the stellar measurements, we approximate the constraints using
a three-dimensional Gaussian in mass, radius, and effective temperature.

@@

\acknowledgements
We thank Roberto Sanchis-Ojeda (Berkeley), Dan Huber (Sydney) and
Jeff Coughlin (SETI) for
conversations and suggestions which improved the quality of this manuscript.
\change{We also thank Keivan Stassun (Vanderbilt) for his insights into 
extinction and stellar parameters in both \kep\ and \KT.
We thank the anonymous referee for their insightful comments as well.}
